New first figure

### 2021-02-10 manuscript/bef_stability/fig1_biomass_network.Rmd
plot_temporal_network properly

source(mypath("R", "misc.R"))
source(mypath("R", "plot_methods.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "press_methods.R"))
source(mypath("R", "synchrony.R"))
source(mypath("R", "community_methods.R"))
source(mypath("R", "community_analysis.R"))
source(mypath("R", "statistical_analysis.R"))
source(mypath("R", "local_network_build.R"))
theme_set(theme_cowplot())
```

@@

  test <- com %>%
    filter(station == 1755)

@@

plot_dyn_web  <- function (com = NULL, sem_df = NULL, station = NULL, stacked =
  FALSE, .log = FALSE) {

@@

@@

```{r}
myload(network_analysis, dir = mypath("data", "classes"))
network_analysis %<>%
  left_join(dplyr::select(op_analysis, opcod, station, year))

net <- get_adj_net_station(net = network_analysis, station = 1755)
net$obs_troph_level_vector[[1]]
net$adj_mat[[1]]
bm <- get_net_biomass(net = network_analysis, station = 1755)
bm$bm[[1]]

@@

## Temporal network

```{r, warning = FALSE, fig.height = 14, fig.width = 14}
par(mfrow = c(2,2))
for (i in seq_along(net$adj_mat)) {
PlotWeb(
  TL = net$obs_troph_level_vector[[i]],
  webTL = net$adj_mat[[i]],
  colnode = set_color_nodes(
    node_list = names(net$obs_troph_level_vector[[i]]),
    color_species_resources = meta_node_color),
  abund = set_node_resources_abun(node_list = names(net$obs_troph_level_vector[[i]]), node_abun = bm$bm[[i]]),
  collink="grey70",
  scale_abun = .2
) 
title(paste0(net$year[[i]]))
}

@@

```{r, warning = FALSE}
list_p <- list()

nb <- seq.int(from = 1, to = length(net$adj_mat), length.out = 4)

p <- ~{ 
par(
  mfrow = c(2,2),
  mar = c(0, 0, 1, 0), 
  mgp = c(2, 1, 0)
)
for (i in nb) {
PlotWeb(
  TL = net$obs_troph_level_vector[[i]],
  webTL = net$adj_mat[[i]],
  colnode = set_color_nodes(
    node_list = names(net$obs_troph_level_vector[[i]]),
    color_species_resources = meta_node_color),
  abund = set_node_resources_abun(node_list = names(net$obs_troph_level_vector[[i]]), node_abun = bm$bm[[i]]),
  collink="grey70",
  scale_abun = .6
)
title(paste0(net$year[[i]]))
p <- recordPlot()
list_p <- c(list_p, p)

}
}

```{r, fig.width = 10, warning = FALSE}
plot_grid(
  plot_dyn_web(com = community_metrics, sem_df = sem_data, station = 1755) +
    theme(legend.position = "bottom"),
  ggdraw(p)
)
```

>>>>

source(mypath("R", "misc.R"))
source(mypath("R", "plot_methods.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "press_methods.R"))
source(mypath("R", "synchrony.R"))
source(mypath("R", "community_methods.R"))
source(mypath("R", "community_analysis.R"))
source(mypath("R", "statistical_analysis.R"))
source(mypath("R", "local_network_build.R"))
theme_set(theme_cowplot())
.pardefault <- par()
```

@@

  st <- station
  test <- com %>%
    filter(station == st)

@@

plot_dyn_web  <- function (com = NULL, sem_df = NULL, station = NULL, stacked =
  FALSE, .log = FALSE, color_species = NULL) {

@@

  if (!is.null(color_species)) {
    p %<>%
      scale_fill_manual(values = meta_node_color) +
      scale_color_manual(values = meta_node_color)
  }

@@

get_network_temporal_plot <- function (
  net_list = NULL,
  station = NULL,
  selected_years = NULL,
  node_color = NULL,
  scale_node_size = 0.01,
  par_options = par(mar = c(0,0,4,0)),
  add_title = FALSE
  ) {

  net <- get_adj_net_station(net = net_list, station = station)
  bm <- get_net_biomass(net = net_list, station = station)

  if (!is.null(selected_years)) {
    net %<>% filter(year %in% selected_years) 
    bm %<>% filter(year %in% selected_years) 
  }

  if (is.null(node_color)) {
    node_color <- set_color_species(
      node_list = unique(names(unlist(net$obs_troph_level_vector))),
      species_list = NULL, resource_list = NULL, col_resource = NULL)
  }

  list_p <- list()
  index <- seq_along(net$year)

  for (i in index) {
    if(!is.null(par_options)) {
      par_options
    }
    plot.new()
    PlotWeb(
      TL = net$obs_troph_level_vector[[index[i]]],
      webTL = net$adj_mat[[index[i]]],
      colnode = set_color_nodes(
	node_list = names(net$obs_troph_level_vector[[index[i]]]),
	color_species_resources = node_color),
      abund = set_node_resources_abun(
	node_list = names(net$obs_troph_level_vector[[index[i]]]),
	node_abun = bm$bm[[index[i]]],
	resource_abun = 1
	),
      collink="grey70",
      scale_abun = scale_node_size,
      rel_abun = FALSE

    )
    if (add_title) {
     title(main = paste0(net$year[[index[i]]]))
    }

    p <- recordPlot()

    list_p[[i]] <- p 
  }

  gg <- map(list_p, ggdraw)
  gg
}
```

```{r}
myload(network_analysis, dir = mypath("data", "classes"))
network_analysis %<>%
  left_join(dplyr::select(op_analysis, opcod, station, year)) %>%
  filter(!is.na(opcod))

net <- get_adj_net_station(net = network_analysis, station = 1755)
bm <- get_net_biomass(net = network_analysis, station = 1755)

@@

```{r, warning = FALSE}
nb <- seq.int(from = 1, to = length(net$adj_mat), length.out = 4)
```

```{r, fig.width = 10}
list_p <- list()
for (i in seq_along(nb)) {
#  par(mar = c(0,0,0,0))
  plot.new()
  PlotWeb(
    TL = net$obs_troph_level_vector[[nb[i]]],
    webTL = net$adj_mat[[nb[i]]],
    colnode = set_color_nodes(
      node_list = names(net$obs_troph_level_vector[[nb[i]]]),
      color_species_resources = meta_node_color),
    abund = set_node_resources_abun(
      node_list = names(net$obs_troph_level_vector[[nb[i]]]),
      node_abun = bm$bm[[nb[i]]],
      resource_abun = 1
      ),
    collink="grey70",
    scale_abun = .01,
    rel_abun = FALSE

  )
#  title(paste0(net$year[[nb[i]]]))

  p <- recordPlot()

  list_p[[i]] <- p 
}

gg <- map(list_p, ggdraw)
plot_grid(plotlist = gg, nrow = 2)
```

```{r}
meta_node_color <- set_color_species(node_list = unique(names(unlist(net$obs_troph_level_vector))), species_list = NULL, resource_list = NULL, col_resource = NULL)

p <- get_network_temporal_plot(net_list = network_analysis, station = 1755,
  selected_years = c(1997, 2010, 2018),
  node_color = meta_node_color, scale_node_size = 0.05, par_options = par(mar = c(1,0,1,0)))
```

```{r, fig.width = 10, fig.height = 12, warning = FALSE}
#par(.pardefault)
#par(.pardefault)
test_p <- plot_grid(
  nrow = 2,
  plot_dyn_web(com = community_metrics, sem_df = sem_data, stacked = TRUE, station = 1755) +
    scale_fill_manual(values = meta_node_color) +
    scale_color_manual(values = meta_node_color)
    ,
  plot_grid(plotlist = p, nrow = 1),
  rel_heights = c(1, 1),
  align = "v"
)

test_p
save_plot(
  "figs/test_temporal_plot.png", test_p,
  nrow = 2, 
  ncol = 1,
  base_height = 4,
  base_width = 8)
```

```{r, eval = FALSE}
test2 <- ggdraw(
  plot_dyn_web(com = community_metrics, sem_df = sem_data, stacked = TRUE, station = 1755)) +
   draw_plot(gg[[1]], .45, .45, .5, .5)

save_plot("figs/test_temporal_plot.png", test2)
```

```{r}
sem_data %>%
  arrange(richness_med, desc(biomass_stab)) %>%
  filter(richness_med >= 3)

@@

```{r}
st <- 21604
te <- plot_dyn_web(com = community_metrics, sem_df = sem_data, station = st, stacked = TRUE)
ti <- get_adj_net_station(net = network_analysis, station = st)

meta_node_color <- set_color_species(
  node_list = unique(names(unlist(ti$obs_troph_level_vector))), 
  species_list = NULL,
  resource_list = NULL,
  col_resource = NULL)

p <- get_network_temporal_plot(net_list = network_analysis, station = st,
  selected_years = c(2007, 2010, 2016),
  node_color = meta_node_color, scale_node_size = 0.02, par_options = par(mar = c(0,0,0,0)))
plot_grid(plotlist = p)

for (i in seq_along(p)) {
  save_plot(paste0("figs/test_net", i, ".png"), p[[i]], base_height = 4, base_width = 4)
}
```

```{r}
test_inc <- ggdraw(te + theme(plot.margin = margin(0, 0, 3, 0, "cm"))) +
  draw_plot(p[[1]], .15, -.01, .2, .2)

  save_plot(paste0("figs/test_net_inc", ".png"), test_inc, base_height = 4)
```
